\bf Landslide: Systematic Testing in 15-410 \\ Sign-Up Sheet

### 2015-02-10 irb/hurdle.tex
update sign up sheet

	\\
	\checkbox{We pass the ``hurdle'' test suite listed in the P2 handout (on at least a vast majority of runs). This includes {\tt startle}, {\tt agility\_drill}, {\tt cyclone}, {\tt join\_specific\_test}, {\tt thr\_exit\_join}.}

	\\
	\checkbox{We have {\em attempted}, but not necessarily pass, the following stress tests; and {\em attempted} to debug and fix any observed bugs: {\tt juggle 4 3 2 0}, {\tt multitest}, {\tt racer} (for 15 minutes), {\tt paraguay}.}

>>>>

	\\
	\checkbox{We pass the ``hurdle'' test suite listed in the P2 handout (on at least a vast majority of runs). This includes {\tt startle}; {\tt agility\_drill}; {\tt cyclone}; {\tt join\_specific\_test}; {\tt thr\_exit\_join}. We acknowledge that {\bf a P2 that cannot pass these tests is incomplete, and Landslide would not work on it at all.}}

	\\
	\checkbox{We have {\em attempted}, but do not necessarily pass, the following stress tests; and {\em attempted} to debug and fix any observed bugs: {\tt juggle 4 3 2 0}; {\tt multitest}; {\tt racer} (for 15 minutes); {\tt paraguay}.}
